Computational Six-bar Synthesis for Implementing Dynamic Behavior

### 2019-02-03 draft.tex
Changed title from "Large Scale Root Finding for the Kinematic Design of Mechanisms with Desired Dynamic Behavior" to "Large Scale Root Finding for Designing Dynamic Machines"
Changed title, added new homotopy-related references

\author{Mark~M.~Plecnik %,~\IEEEmembership{Member,~IEEE,}
        and~Ronald~S.~Fearing,~\IEEEmembership{Member,~IEEE}% <-this % stops a space
\thanks{M.~Plecnik is an assistant professor in the Department of Aerospace and Mechanical Engineering at the University of Notre Dame, IN, 46556 USA e-mail: {\tt\small plecnikmark@nd.edu}}% <-this % stops a space
\thanks{R.~S.~Fearing is director of the Biomimetic Millisystems Lab and a professor in the Department of Electrical Engineering \& Computer Science, University of California, Berkeley, CA, 94720 USA e-mail: {\tt\small ronf@eecs.berkeley.edu}}% <-this % stops a space
\thanks{Manuscript received January xx, 2019; revised Month xx, 2019.}}

@@

The role of homotopy continuation methods in mechanism design traces back to Roth and Freudenstein's bootstrap method \cite{rothSynthesisPathGeneratingMechanisms1963}. %
After that, more general methods focused on constructing homotopy paths absent of turning points or intersections \cite{zangwillPathwaysSolutionsFixed1981}, handling infinite roots by tracking in projective spaces \cite{wrightFindingAllSolutions1985}, and computing singular endpoints \cite{morganPowerSeriesMethod1992}. %
Additionally, researchers were interested in increasing the efficiency of computing large root sets by limiting the number of homotopy paths that need to be tracked. %
The work of Morgan and Sommese \cite{morganHomotopySolvingGeneral1987} lead to \emph{multihomogeneous homotopies} that take advantage of sparse monomial structures.  Variables are split into groups that define a factored start system of fewer roots, reducing the number of homotopy paths to track. %
Generalizations of this work lead to partitioned linear product homotopy \cite{verscheldeGBQAlgorithmConstructing1993,wiseAlgorithm801POLSYS2000}, general linear product homotopy \cite{verscheldeSymbolicHomotopyConstruction1993,verscheldeAlgorithm795PHCpack1999,suAlgorithm857POLSYS2006}, and polyhedral homotopy \cite{verscheldeHomotopiesExploitingNewton1994}. %
Hauenstein et al. \cite{hauensteinRegenerationHomotopiesSolving2011} introduced regeneration homotopy, an efficient method that exploits the sparse monomial structure of a system one equation at a time to find all of its isolated solutions. %
Plecnik and Fearing \cite{plecnikFindingOnlyFinite2017,plecnikStudyFindingFinite2017} introduced the Finite Root Generation method for solving mechanism synthesis equations.  
This is the solution technique used in this paper.  It institutes a stochastic procedure for generating startpoints that always track to finite roots.

@@

@@

\begin{table}[h]
\caption{Specification of $\mathbf{q}_\text{task}$ for the leg mechanism example.}
\label{task_parameters}
\centering
\begin{tabular}{c|r@{}lc}
$j$ & \multicolumn{2}{c}{$P_j$ (cm)} & \multicolumn{1}{c}{$\phi_j$ (rad)} \\
\hline
0 & 0.09504886 & $+$0.06372449$i$ & 0 \\
1 & 0.90856802 & $-$0.19472945$i$ & 0.04956958 \\
2 & 1.90242974 & $-$0.28657681$i$ & 0.11939315 \\
3 & 3.52297908 & $-$0.26708542$i$ & 0.35571795 \\
4 & 5.13673683 & $-$0.11927755$i$ & 0.99925301 \\
5 & 4.18184656 & $+$0.74327464$i$ & 2.29135153 \\
6 & 2.19553111 & $+$1.48251591$i$ & 4.08970859 \\
7 & 0.60702434 & $+$1.66736265$i$ & 5.46542362 \\
\end{tabular}
\end{table}

\begin{figure}[!t]
\centering
\includegraphics[scale=0.5]{root_histogram}
\caption{Condition numbers of Jacobian matrices at the solutions found during the leg mechanism example.  We assume solutions with condition numbers greater than $10^{15}$ are singular.}
\label{root_histogram}
\end{figure}

@@

\begin{figure}[!t]
\centering
\includegraphics[scale=0.3]{prototype_overlay}
\caption{The linkage drawn in Fig. \ref{synth_results}a was constructed.}
\label{prototype_overlay}
\end{figure}

@@

The authors kindly thank Katherine Fearing for construction of the prototype linkage.

We gratefully acknowledge the support of the National Science Foundation through award CMMI-1636302.  Any opinions, findings, and conclusions or recommendations expressed in this material are those of the authors and do not necessarily reflect the views of the National Science Foundation.

>>>>

\title{Large Scale Root Finding for \\ Designing Dynamic Machines}

\title{Designing Dynamic Machines \\ Using Large Scale Root Finding}

\author{Mark~M.~Plecnik %,~\IEEEmembership{Member,~IEEE,}
        and~Ronald~S.~Fearing,~\IEEEmembership{Member,~IEEE}% <-this % stops a space
\thanks{M.~Plecnik is with the Department of Aerospace and Mechanical Engineering, University of Notre Dame, IN, 46556 USA e-mail: {\tt\small plecnikmark@nd.edu}}% <-this % stops a space
\thanks{R.~S.~Fearing is with the Department of Electrical Engineering and Computer
Sciences, University of California, Berkeley, CA 94720 USA e-mail: {\tt\small ronf@eecs.berkeley.edu}}% <-this % stops a space
\thanks{Manuscript received February xx, 2019; revised Month xx, 2019.}}

@@

The role of homotopy continuation methods in mechanism design traces back to Roth and Freudenstein's bootstrap method \cite{rothSynthesisPathGeneratingMechanisms1963}. %
After that, more general methods focused on constructing homotopy paths absent of turning points or intersections \cite{zangwillPathwaysSolutionsFixed1981}, handling infinite roots by tracking in projective spaces \cite{wrightFindingAllSolutions1985}, and computing singular endpoints \cite{morganPowerSeriesMethod1992}. %
Additionally, researchers were interested in increasing the efficiency of computing large root sets by limiting the number of homotopy paths that need to be tracked. %
The work of Morgan and Sommese \cite{morganHomotopySolvingGeneral1987} lead to \emph{multihomogeneous homotopies} that take advantage of sparse monomial structures.  Variables are split into groups that define a factored start system of fewer roots, reducing the number of homotopy paths to track. %
Generalizations of this work lead to partitioned linear product homotopy \cite{verscheldeGBQAlgorithmConstructingStart1993,wiseAlgorithm801POLSYS2000}, general linear product homotopy \cite{verscheldeSymbolicHomotopyConstruction1993,verscheldeAlgorithm795PHCpack1999,suAlgorithm857POLSYS2006}, and polyhedral homotopy \cite{verscheldeHomotopiesExploitingNewton1994,huberPolyhedralMethodSolving1995,leykinPolyhedralHomotopies2019}. %
As well, methods have been developed to validate numerical representations of solution sets \cite{hauensteinAlgorithm921AlphaCertified2012,leykinTraceTest2018}.

To find complete sets of roots more efficiently Hauenstein et al. \cite{hauensteinRegenerationHomotopiesSolving2011} introduced regeneration homotopy, which exploits the sparse monomial structure of a system one equation at a time to find all of its isolated solutions. %
Plecnik and Fearing \cite{plecnikFindingOnlyFinite2017,plecnikStudyFindingFinite2017} introduced the Finite Root Generation (FRG) method for collecting the roots of mechanism synthesis systems.  FRG quickly generates startpoints and start systems that track only to finite endpoints, eliminating expensive homotopy paths that diverge to infinity. %
Baskar and Bandyopadhyay \cite{baskarAlgorithmComputeFinite2019} introduced a technique for collecting roots by tracking homotopy paths between two generic systems.  They generate new roots by permuting the correspondence between solutions at every iteration. %
Duff et al. \cite{duffSolvingPolynomialSystems} developed a monodromy solver which tracks homotopy paths along the edges of a graph embedded in the parameterized space of a target polynomial system.
By retracing edges and keeping track of the correspondence of roots at each vertex, they are able to collect roots in a more efficient manner. %

@@

\begin{table}[t]
\caption{Specification of $\mathbf{q}_\text{task}$ for the leg mechanism example.}
\label{task_parameters}
\centering
\begin{tabular}{c|r@{}lc}
$j$ & \multicolumn{2}{c}{$P_j$ (cm)} & \multicolumn{1}{c}{$\phi_j$ (rad)} \\
\hline
0 & 0.09504886 & $+$0.06372449$i$ & 0 \\
1 & 0.90856802 & $-$0.19472945$i$ & 0.04956958 \\
2 & 1.90242974 & $-$0.28657681$i$ & 0.11939315 \\
3 & 3.52297908 & $-$0.26708542$i$ & 0.35571795 \\
4 & 5.13673683 & $-$0.11927755$i$ & 0.99925301 \\
5 & 4.18184656 & $+$0.74327464$i$ & 2.29135153 \\
6 & 2.19553111 & $+$1.48251591$i$ & 4.08970859 \\
7 & 0.60702434 & $+$1.66736265$i$ & 5.46542362 \\
\end{tabular}
\end{table}

@@

\begin{figure}[!t]
\centering
\includegraphics[scale=0.5]{root_histogram}
\caption{Condition numbers of Jacobian matrices at the solutions found during the leg mechanism example.  Solutions with condition numbers greater than $10^{15}$ were assumed to be singular.}
\label{root_histogram}
\end{figure}

@@

\begin{figure}[!t]
\centering
\includegraphics[scale=0.3]{prototype_overlay}
\caption{Construction of the linkage drawn in Fig. \ref{synth_results}a.}
\label{prototype_overlay}
\end{figure}

@@

The authors kindly thank Katherine Fearing for construction of the prototype linkage.
We gratefully acknowledge the support of the National Science Foundation through award CMMI-1636302.  Any opinions, findings, and conclusions or recommendations expressed in this material are those of the authors and do not necessarily reflect the views of the National Science Foundation.
